Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-10-12 paper.tex
Simplify

Anyone who has ever read a cryptography paper knows this for a fact:
cryptographers are at the top of the academic thought chain. In the
archetypal symmetric cryptography paper, there is a ``Section 2''
scene in which cryptographers are bravely waving their most potent
finite field. In a latter ``Section 4'' scene, the very same
cryptographers are seen extolling the virtues of some nifty
\textsc{Arm} Cortex assembly instruction, which takes center stage in
their hand-crafted, manually optimized implementation. No wonder we
jealously stash them away in ``zone à régime restrictive''! The rumor
goes that, behind these padlocked doors, they have developed a set of
domain-specific techniques to deliver very high-throughput software
implementation of symmetric ciphers. This has been slowly gnawing at
compiler writers, for whom job
security~\citep{bernstein:death-compiler,venkatesh:compiler-security}
has become a major concern. Luckily for us, every now and then,
someone inadvertently let the genies out of their Klein bottle and we
get to read about the subtle art of
``bitslicing''~\citep{biham:DES} and
``fixslicing''~\citep{adominicai:fixslicing-gift,
  adomnicai:fixslicing-AES-like}.

>>>>

Anyone who has ever read a cryptography paper knows this for a fact:
cryptographers are at the top of the academic thought chain. In the
archetypal symmetric cryptography paper, there is a ``Section 2''
scene in which cryptographers are bravely waving their most potent
finite field. In a latter ``Section 4'' scene, the very same
cryptographers are seen extolling the virtues of some nifty
\textsc{Arm} Cortex assembly instruction, which takes center stage in
their hand-crafted, manually optimized implementation. No wonder we
jealously stash them away in ``zone à régime restrictive''! The rumor
goes that, behind these padlocked doors, they have developed a set of
domain-specific techniques to deliver high-throughput software
implementation of symmetric ciphers. This has been slowly gnawing at
compiler writers, for whom job
security~\citep{bernstein:death-compiler,venkatesh:compiler-security}
has become a major concern. Luckily for us, every now and then,
someone inadvertently let the genies out of their Klein bottle and we
get to read about the subtle art of ``bitslicing''~\citep{biham:DES}
and ``fixslicing''~\citep{adominicai:fixslicing-gift,
  adomnicai:fixslicing-AES-like}.
